Setting up Data

### 2019-10-08 src/SetupData.Rmd
removed pointless table
removed Peromyscus notes from meta file

#forgot why I'm reading in this metadata file
meta.data = read.csv("data/clean.Meta.Data.txt",sep = "\t", header=TRUE)
MLH1_data = read.csv("data/MLH1/AnonData.csv", header=TRUE)

@@

#male_mouse_table_w.good.ages

>>>>

#forgot why I'm reading in this metadata file
meta.data = read.csv("data/clean.Meta.Data.txt",sep = "\t", header=TRUE)
#remove all MAD (peromyscus) from meta.data
meta.data <- meta.data[ !grepl("MAD", meta.data$mouse) , ]

MLH1_data = read.csv("data/MLH1/AnonData.csv", header=TRUE)

@@

#male_mouse_table_w.good.ages
```
